---
title: "311 sample play"
author: "Hannah"
date: "Wednesday, February 10, 2016"
output: html_document
---



```{r,echo=FALSE}
library(plyr)
library(dplyr)
library(ggplot2)
##change fig height
##normalize by pop (income dist)
##Redo to pull from github

#setwd('../Desktop')
  sample  <- read.csv("cases_sample.csv")
  
  acs <- read.csv("ACS_14_5YR_B19301_with_ann.csv",header=TRUE,skip = 1)
  
  dfn <- read.csv("ACS_14_5YR_B19301_metadata.csv")

#Cleaning
    names(acs) <- c("Id", "Census.Block","Geography", "pc_inc2014","pc_inc2014_err")
        
  #Calculate case length
  ##CHECK LATER: Make sure you're converting AM/PM correctly
    sample$Opened <- strptime(sample$Opened, format="%m/%d/%Y %H:%M:%S %p")
    sample$Closed <- strptime(sample$Closed, format="%m/%d/%Y %H:%M:%S %p")
    sample$caselength <- ifelse(sample$Status == 'Closed',
                                difftime(as.POSIXct(sample$Closed), as.POSIXct(sample$Opened),units="hours"),
                                "NA") 
    sample$caselength <- as.numeric(sample$caselength)
    sample$casedays <- sample$caselength/24
  
  #Align merge IDs
    sample %>% transmute(as.integer(Census.Block))
  
  #Merge sample with ACS data
    income <- join(sample,acs,by = "Census.Block" , type = "left", match = "all")

  #Convert income from factor to numeric first
    income$pc_inc2014 <- as.numeric(paste(income$pc_inc2014))
    income$pc_inc2014_err <- as.numeric(paste(income$pc_inc2014_err))

```

```{r, echo=FALSE,fig.height=6, fig.width=8}
#Standard errors are large
plot_1 <- ggplot(data=income, aes(x=pc_inc2014, y=abs(pc_inc2014_err))) + geom_point()
plot_1

#See how factor variables predict income

  lm1 <- lm(pc_inc2014~caselength, data = income)
  summary(lm1)
  lm2 <- lm(pc_inc2014~Source, data = income)
  summary(lm2)
  lm3 <- lm(pc_inc2014~Neighborhood, data = income)
  summary(lm3)
  lm4 <- lm(pc_inc2014~Request.Type, data = income)
  summary(lm4)
  
  lm5 <- lm(pc_inc2014~Neighborhood + Source + Request.Type, data = income)
  summary(lm5)
```

As we might expect, neighborhood is a significant predictor of income. Controlling for neighborhood and source, other significant predictors to note:
    *Request for new street light significantly predicts income at the 5% level with a coefficient of almost $70k.
    *Request for service from the port authority significantly predicts income at the 10% level with a coefficient of $51k.
    *Request type other with detail significantly predicts income at the 5% level with a coefficient of $74k.
    *Customer callback for traffic engineering is negatively and significantly correlated with income.
    *Complaints to the entertainment commission are negatively and significantly correlated with income.
    
    
```{r}
##Confirm significant differences in income between factor levels with anova tests

  aov1 = aov(income$pc_inc2014 ~ income$Neighborhood)
  summary(aov1)
  
  aov2 = aov(income$pc_inc2014 ~ income$Source)
  summary(aov2)
  
  aov3 = aov(income$pc_inc2014 ~ income$Responsible.Agency)
  summary(aov3)
  
  aov4 = aov(income$pc_inc2014 ~ income$Request.Type)
  summary(aov4)
```
 The differences in income between factor levels in the Neighborhood, Responsible Agency, Source, and Request Type variables are significant.
 
```{r}
#Visually confirm that income and caselength not correlated
  
  line_1 <- ggplot(data=income, aes(x=pc_inc2014, y=casedays, group=1))
  line_1 + geom_point(aes(color=factor(Source)))

#Visually show income distribution by source 
  box_1 <- ggplot(data=income,aes(x=pc_inc2014, fill = Source, color=Source)) 
  box_1 +  geom_histogram(aes(x=pc_inc2014, fill=Source),binwidth=20000) + facet_wrap( ~ Source, ncol=1)  + geom_density()

#Rich people don't use 311
  
  dens_1 <- ggplot(income, aes(x=pc_inc2014)) 
  dens_1 + geom_density()
  
#Visually show income distribution by request type
  req_fac <- model.matrix(~Request.Type, data = income)
  factors <- cbind(income[,"pc_inc2014"],req_fac[,3:255])

  plot <- function(fac) {
      ggplot(data=factors,aes(x=pc_inc2014, fill = fac, color=fac))  +  geom_histogram() 
                         }
  collist <- as.list(names(factors))
  
#  lapply(collist, plot(fac))



##could categorize income do chi square test
##tukey multiple comparison



```


```{r}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
