---
title: "311 sample play"
author: "Hannah"
date: "Wednesday, February 24, 2016"
output: html_document
---



```{r,echo=FALSE, results='hide',warning=FALSE}
library(dplyr)
library(ggplot2)
library(stargazer)
##Redo to pull from github

setwd("C:/Users/HBurak/Documents/Hannah's stuff/data-science-wg/projects-in-this-repo/311_Exploratory-Analyses")
  sample  <- read.csv("cases_sample.csv")
  
  acs <- read.csv("ACS_14_5YR_B19301_with_ann.csv",header=TRUE,skip = 1)
  
  dfn <- read.csv("ACS_14_5YR_B19301_metadata.csv")

  population <- read.csv("sf_neighborhood-census-profile.csv")

    #sf_fips <- read.csv("C:/Users/HBurak/Downloads/Analysis_Neighborhoods.csv")
    #names(sf_fips)[names(sf_fips)=="GEOID"] <- "Census.Block"
  #See if missing FIPS blocks
    #missingblocks <- join(sample,sf_fips,by="Census.Block", type="full")
    #tempsample <- sample
    #tempsample$Census.Block <- as.character(tempsample$Census.Block)
    #tempsample$Census.Block <- substr(tempsample$Census.Block, 1, nchar(tempsample$Census.Block)-1)
    #tempsample$Census.Block  <- as.numeric(tempsample$Census.Block)
    #missingblock <- merge(tempsample,sf_fips,by.x="Census.Block",by.y="Census.Block",all=TRUE)

#Cleaning
    names(acs) <- c("Id", "Census.Block","Geography", "pc_inc2014","pc_inc2014_err")
        
  #Calculate case length
  ##CHECK LATER: Make sure you're converting AM/PM correctly
    sample$Opened <- strptime(sample$Opened, format="%m/%d/%Y %H:%M:%S %p")
    sample$Closed <- strptime(sample$Closed, format="%m/%d/%Y %H:%M:%S %p")
    sample$caselength <- ifelse(sample$Status == 'Closed',
                                difftime(as.POSIXct(sample$Closed), as.POSIXct(sample$Opened),units="hours"),
                                "NA") 
    sample$caselength <- as.numeric(sample$caselength)
    sample$casedays <- sample$caselength/24
  
  #Align merge IDs
    sample %>% transmute(as.integer(Census.Block))
  
  #Merge sample with ACS data
    income <- merge(sample,acs,by = "Census.Block" , type = "left", match = "all")

  #Convert income from factor to numeric and supervisor district to factor
    income$pc_inc2014 <- as.numeric(paste(income$pc_inc2014))
    income$pc_inc2014_err <- as.numeric(paste(income$pc_inc2014_err))
    income$Supervisor.District <- as.factor(income$Supervisor.District)

    income <- income[,4:30]

  #Create dataset with a weight to normalize by population
  
    normal <- join(income,population, by = "Neighborhood", type = "left", match = "all")
    counts <- as.data.frame(table(normal$Neighborhood))
    names(counts) <- c("Neighborhood","Frequency")
    normal <- join(normal,counts, by = "Neighborhood", type = "left", match = "all")

    normal <- normal %>%
                select(Neighborhood,Total.Pop,Responsible.Agency, Request.Type,Supervisor.District,
                        Source,Census.Block,caselength,casedays,pc_inc2014,pc_inc2014_err,Frequency,Category) %>%
                mutate(calldens = Frequency/Total.Pop)
        

```


Before we dive into analysis, please note the very large standard errors associated with the income variable.
```{r,echo=FALSE,fig.height=6, fig.width=8}
#Standard errors are large
plot_1 <- ggplot(data=income, aes(x=pc_inc2014, y=abs(pc_inc2014_err))) + geom_point()
plot_1

```
##Predicting income
```{r, echo=FALSE,results='asis'}

#See how factor variables predict income
  lm1 <- lm(pc_inc2014~caselength, data = income)
  stargazer(lm1,type="html", style = "aer", title="Using caselength to predict income")
  lm2 <- lm(pc_inc2014~Source, data = income)
  stargazer(lm2,type="html", style = "aer", title="Using request source to predict income")
  lm3 <- lm(pc_inc2014~Neighborhood, data = income)
  stargazer(lm3,type="html", style = "aer",title="Using neighborhood to predict income")
      lm_normal <- lm(pc_inc2014~Neighborhood + Total.Pop, data = normal)
      stargazer(lm_normal,type="html",style = "aer", 
                title="Using neighborhood to predict income, controlling for neighborhood population")
  lm4 <- lm(pc_inc2014~Request.Type, data = income)
  stargazer(lm4,type="html", style = "aer",title="Using request type to predict income")
  lm5 <- lm(pc_inc2014~Supervisor.District, data = income)
  stargazer(lm5,type="html", style = "aer",title="Using supervisor district to predict income")
  lm6 <- lm(pc_inc2014~Category, data = income)
  stargazer(lm6,type="html", style = "aer",title="Using request category to predict income")

#predicting call density with income

  lm11 <- lm(pc_inc2014~calldens,data = normal)
  stargazer(lm11,type="html",style = "aer",title="Using call density to predict income")

```


```{r,echo=FALSE,results='hide'}
#probably way too many covariates on these--would be great to categorize on a higher level
  lm7 <- lm(pc_inc2014~Neighborhood + Source + Responsible.Agency, data = income)
  stargazer(lm7,type="html",style = "aer",title="Using responsible agency to predict income, controlling for neighborhood and source")
  lm8 <- lm(pc_inc2014~Neighborhood + Source + Request.Type, data = income)
  stargazer(lm2,lm3,lm8,type="html",title="Using request type to predict income, controlling for neighborhood and source")
  lm9 <- lm(pc_inc2014~Neighborhood + Source + Responsible.Agency + Total.Pop , data = normal)
  stargazer(lm9, type="html", title="Using Neighborhood, source, and responsible agency and total population")
  lm10 <- lm(pc_inc2014~Neighborhood + Category, data = income)
  stargazer(lm10,type="html",style = "aer",title="Using category to predict income, controlling for neighborhood")

```

As we might expect, neighborhood is a significant predictor of income and has the most explanatory power for income variation. Other factors we looked at do not have much significance or explanatory power. 

*Controlling for neighborhood and source, a few other significant predictors to note:
  +Request for new street light significantly predicts income at the 5% level with a coefficient of almost $70k.
  +Request for service from the port authority significantly predicts income at the 10% level with a coefficient of $51k.
  +Request type other with detail significantly predicts income at the 5% level with a coefficient of $74k.
  +Customer callback for traffic engineering is negatively and significantly correlated with income.
  +Complaints to the entertainment commission are negatively and significantly correlated with income.
  +A request to the Streetlight Hold Queue agency is significantly correlated with income, but request to Streetlight               Queue is not.
  +Requests to the Water Waste Queue agency are positively correlated.
    
    Note: Run in R for full regression tables.
    
##Differences between factor levels

 The differences in income between factor levels in the Neighborhood, Responsible Agency, Source, and Request Type variables are significant.
 
```{r}
##Confirm significant differences in income between factor levels with anova tests

  aov1 = aov(income$pc_inc2014 ~ income$Neighborhood)
  summary(aov1)
  
  aov2 = aov(income$pc_inc2014 ~ income$Source)
  summary(aov2)
  
  aov3 = aov(income$pc_inc2014 ~ income$Responsible.Agency)
  summary(aov3)
  
  aov4 = aov(income$pc_inc2014 ~ income$Request.Type)
  summary(aov4)

  aov5 = aov(income$pc_inc2014 ~ income$Category)
  summary(aov5)

```


##Plots

```{r}
#Visually confirm that income and caselength not correlated
 options(warn=-1) 

  line_1 <- ggplot(data=income, aes(x=pc_inc2014, y=casedays, group=1))
  line_1 + geom_point(aes(color=factor(Source)))
```

```{r,fig.height=12, fig.width=10}
#Visually show income distribution by source 

  box_1 <- ggplot(data=income,aes(x=pc_inc2014, fill = Source, color=Source)) 
  box_1 + geom_histogram(aes(x=pc_inc2014, fill=Source),binwidth=20000) + facet_wrap( ~ Source, ncol=1)  + geom_density()
```

```{r}
#Rich people don't use 311
  
  dens_1 <- ggplot(income, aes(x=pc_inc2014)) 
  dens_1 + ggtitle("Calls by income") + geom_density() 

  dens_2 <- ggplot(normal, aes(x=pc_inc2014, fill = calldens)) 
  dens_2 + ggtitle("Call density by income") + geom_density()

```

```{r,fig.height=12, fig.width=10}
#Income varies by supervisor district
 
  box_2 <- ggplot(data=income,aes(x=pc_inc2014, fill = Supervisor.District, color=Supervisor.District)) 
  box_2 + geom_histogram(aes(x=pc_inc2014, fill=Supervisor.District),binwidth=20000) + 
        facet_wrap( ~ Supervisor.District, ncol=1)  + geom_density()

```

```{r,fig.height=10, fig.width=10}
#Call density vs income

  dens_3 <- ggplot(data=normal, aes(x=pc_inc2014,y=calldens))
  dens_3 + geom_point(aes(color=factor(Supervisor.District))) + guides(fill=FALSE)

options(warn=0)

```

```{r}
topcats <- normal[normal$Category,]

```

```{r}
#Top request categories

 topcats <-  normal %>%
                select(Category,pc_inc2014) %>%
                group_by(Category) %>%
                mutate(count=n()) 
topcats <- topcats[topcats$count > 180,]
topcats %>%
  group_by(Category) %>%
  summarize(counts=n()) %>%
  arrange(-counts)

  bar_1 <- ggplot(data=topcats,aes(x=pc_inc2014, fill = Category, color=Category)) 
  bar_1 + geom_histogram(aes(x=pc_inc2014, fill=Category),binwidth=20000) + facet_wrap( ~ Category, ncol=1)  + geom_density()


```
